Simple Wind Models

### 2010-07-24 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5064 ac11df5e-a788-c23b-a8e1-c758c323924d
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5072 ac11df5e-a788-c23b-a8e1-c758c323924d

 \begin{enumerate}
   \item Peak optical depth
     \begin{itemize}
       \item Not a robust measure of $\tau_{wind}$
       \item Not even a good relative predictor for $\tau$
       \item Not a robust predictor of $f_c$
     \end{itemize}
   \item Kinematics
     \begin{itemize}
       \item Nearly robust for $v<v_{min}$
       \item But what sets $v_{min}$?
       \item Generally get the full extent of the wind speed
     \end{itemize}
   \item EW
     \begin{itemize}
       \item Primarily set by $v_{min}(\tau \sim 1)$
       \item $f\lambda$ matters, but so do emission channels
     \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Distance to the source
     \end{itemize}
 \end{enumerate}

@@

 \begin{enumerate}
   \item Resonant lines
     \begin{itemize}
       \item Kinematics of backside
       \item Flux + relative
    \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Flux $\propto \tau_{wind}$ + relative
       \item Kinematics (anisotropy)
    \end{itemize}
 \end{enumerate}

@@

>>>>

 \begin{enumerate}
   \item Peak optical depth
     \begin{itemize}
       \item Not a robust measure of $\tau_{wind}$
       \item Not even a good relative predictor for $\tau$
       \item Not a robust predictor of $f_c$
       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
     \end{itemize}
   \item Kinematics
     \begin{itemize}
       \item Nearly robust for $v<v_{min}$
       \item But what sets $v_{min}$?
       \item Generally get the full extent of the wind speed
       \item Plot $v_{pk}$ vs $\tau_{pk}$
     \end{itemize}
   \item EW
     \begin{itemize}
       \item Primarily set by $v_{min}(\tau \sim 1)$
       \item $f\lambda$ matters, but so do emission channels
       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
     \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Distance to the source
     \end{itemize}
 \end{enumerate}

@@

 \begin{enumerate}
   \item Resonant lines
     \begin{itemize}
       \item Kinematics of backside
       \item Flux + relative
       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
    \end{itemize}
   \item Fine-structure
     \begin{itemize}
       \item Flux $\propto \tau_{wind}$ + relative
       \item Kinematics (anisotropy)
    \end{itemize}
 \end{enumerate}

@@

1)  Emission is a generic prediction of wind models (and something
which has been essentially ignored aside from \lya).  We can discuss
the caveats (dust, finite slit size, intrinsic spectrum).

2)  Emission complicates the analysis of absorption at v$\sim$0 km/s, especially in
resonantly trapped transitions (e.g. MgII, NaI).   This affects tau\_pk,
C\_f and also offsets the line centroids (e.g. FeII, MgII).  These
are primarily negative effects.

3)  Emission can be used for good!   This is largely an extension of
your emission paper, of course.

   (i)  Morphology [MgII is likely best]
  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
 (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
